Legacy Data Confounds Modern Genomics Studies

### 2019-06-25 PlottingScripts/ProcessPlotData.Rmd
Updated figure 1 with pluralization and finalized significance test.

#toggle for all snps or just JPT 1kGP snps
name <- 'strict.gcat.' #'gcat.' # ''

@@

rSNP <- read.table(paste0(DataPath, name,
                          'random.pos.context.txt'), 
                sep = '\t',
                header = FALSE,
                col.names = contextHeader)

@@

SNP <- processContext(SNP)
rSNP <- processContext(rSNP)

>>>>

#toggle for all snps or just JPT 1kGP snps
name <-''#'strict.gcat.' #'gcat.' # '' #

@@

rSNP <- read.table(paste0(DataPath,'GenomeWide.AncestralContext.txt'), 
                sep = '\t',
                header = FALSE,
                col.names = contextHeader)

@@

SNP <- processContext(SNP)

rSNP <- processContext(rSNP)
rSNP <- 
  rSNP %>%
  filter(Start != "N" &
           End != "N")

#get proportions
total_count <- sum(rSNP$Freq)
total_sample <- sum(SNP$Freq)
rSNP$Freq <- rSNP$Freq / total_count * total_sample
